---
title: "Application_Timing"
author: "Meghan Duffy"
date: "February 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question: Is there a difference in when men and women first apply for jobs?
Analysis was suggested by an anonymous postdoc, who noted that there appears to be a difference in when men and women first apply for faculty positions, based on data in the 2016-2017 job wiki. First, let's recreate that figure, using a version of the "anonymous qualifications" page downloaded on February 26, 2017 from:
https://docs.google.com/spreadsheets/d/1rOjzt71IBfaz5gYuiVyJxzoCAD8WqM39eUjUhgBEFuU/edit#gid=1893361791

For "# years in postdoc" column:
Changed the "< 1" to "0.5"
Changed a "4 + 2 as RA" to 6
Changed "3 + 14 alt-ac" to NA

For "# 1st author peer-reviewed papers" column:
Changed "13 journal + 15 conference" to NA

For other papers column:
Changed "19 journal + 8 conference" to NA

For major grants column:
Changed "0 (2 if you count fellowships)" to 0

For years on market:
Changed "< 1" to "0.5"

For number applications:
removed ~ and just went with number they said
for anything else, changed to NA

```{r,load libraries,message=FALSE,echo=FALSE}
library(ggplot2)
library(dplyr)
library(cowplot)
library(stringr)
```

```{r, load data}
df <- read.csv("EcoEvoJobApps20162017AnonQualsedited.csv", na.strings = "?")
head(df)
colnames(df)
str(df)
```
### Make figure based on one that was sent to me (Year PhD of applicants by gender)
```{r, plot year Phd of applicants}
YearGender <- 
  df %>%
  filter(!is.na(Postdoc)) %>%
  filter(Number.apps >0) %>%
  group_by(Gender,Postdoc) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

yeargenderplot <- df %>%
  filter(!is.na(Postdoc)) %>%
  filter(Number.apps >0) %>%
  ggplot(aes(x = Postdoc, fill=Gender)) +
  geom_histogram(binwidth=1.0, boundary=-0.5, position="dodge") +
  xlab("Year of PhD") +
  theme_bw() 

yeargenderplot

save_plot("yeargenderplot.jpg", yeargenderplot)
```

### Looking at years on market
```{r, years on market plot}
yearsonmarketplot <- df %>%
  filter(!is.na(Years.on.market)) %>%
  ggplot(aes(x = Years.on.market, fill=Gender)) +
  geom_histogram(binwidth=1.0, boundary=-0.5, position="dodge") +
  xlab("Years on market") +
  theme_bw() 

yearsonmarketplot
```

### Does the year gender plot pattern hold for 2015-2016?
```{r, load 2015-2016 data}
df2015 <- read.csv("EcoEvoJobApps20152016AnonQualsedited.csv", na.strings = "?")
head(df)
colnames(df)
str(df)
```

```{r, plot year Phd for 2015-2016}
YearGender2015 <- 
  df2015 %>%
  filter(!is.na(PhD.year)) %>%
  filter(Number.apps >0) %>%
  group_by(Gender,PhD.year) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

yeargenderplot2015 <- df2015 %>%
  filter(!is.na(PhD.year)) %>%
  filter(!is.na(Gender)) %>%
  filter(Number.apps >0) %>%
  ggplot(aes(x = PhD.year, fill=Gender)) +
  geom_histogram(binwidth=1.0, boundary=-0.5, position="dodge") +
  xlab("Year of PhD") +
  theme_bw() 

yeargenderplot2015

save_plot("yeargenderplot2015.jpg", yeargenderplot2015)
```